% AWARDS
\vspace{0.5 mm}
\cvsection{\faTrophy \hspace{0.3cm} Awards}
\begin{itemize}
\item Best Work in "Practical studies of 3D modeling and Virtual Reality using Blender" during the 3rd edition of Encontros Universitários at the Federal University of Ceará - Crateús Campus.
\smallskip
\item Champion of Slam do 13 (June 2016 edition) in the short poems category.
\end{itemize}

% SKILLS
\cvsection{\faCoffee \hspace{0.3cm}Knowledge}
\begin{itemize}
\item Programming languages:
\end{itemize}
\cvtag{C}
\cvtag{Java}
\cvtag{C++}
\cvtag{JavaScript}
\cvtag{Python}

\vspace{2.5 mm}

\begin{itemize}
\item Mobile and Web development:
\end{itemize}
\cvtag{HTML}
\cvtag{CSS}
\cvtag{ReactJS}
\cvtag{TypeScript}
\cvtag{MySQL}
\cvtag{Android}
\cvtag{Firebase}

\vspace{2.5 mm}

\begin{itemize}
\item Graphic Design:
\end{itemize}
\cvtag{Photoshop}
\cvtag{Blender}
\cvtag{Inkscape}
\cvtag{Figma}

\vspace{2.5 mm}

\begin{itemize}
\item Soft skills:
\end{itemize}
\cvtag{Communication}
\cvtag{Teamwork}

\vspace{3 mm}

% BOOKS
\cvsection{\faBook \hspace{0.3cm} Publications}
\cvevent{A LER VAZIOS}{Compilation of poetic-visual experiments.}{2016}{}
\smallskip
\cvevent{PROTESTIZANDO}{Compilation of poems.}{2015}{}
\smallskip
\cvevent{ANTHOLOGIES}{}{}{}
\begin{itemize}
\item Poesia na Faixa (Poetas do Tietê)
\item 180 gramas (Sarau do Vinil)
\end{itemize}

% PROJECTS
\cvsection{\faStar \hspace{0.3cm} Projects}

%\cvevent{CURRENT PROJECTS}{}{}{}
\cvevent{HáLUGAR (Mobile Development)}{Housing app for students. Available on Play Store.}{}{}
\smallskip
\cvevent{ALUMINIONS (Visual Arts)}{Creation of characters using aluminum seals.}{}{}
\smallskip
\cvevent{YOUTUBE CHANNEL (Education)}{Programming tutorials for beginners.}{}{}
\smallskip
\cvevent{COMPIXELAR (Creative Coding)}{Development of multimedia experiments using Processing.}{}{}