% References:
% Icons: http://mirrors.ibiblio.org/CTAN/fonts/fontawesome/doc/fontawesome.pdf

%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage[document]{ragged2e}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Hyperlink style
\hypersetup{
    colorlinks=false,
    linkcolor=black,
    urlcolor=blue,
}

% Divider
\RequirePackage{xcolor}
\RequirePackage{dashrule}
\colorlet{body}{black!80!white}
\newcommand{\divider}{\textcolor{body!30}{\hdashrule{\linewidth}{0.5pt}{0.7ex}}\medskip}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

% Better adjustment
\usepackage[margin=0.5in]{geometry}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
    \item \small{\textbf{#1}{ #2 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
        \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
            \textbf{#1} & #2 \\
            \textit{\small#3} & \small #4 \\
        \end{tabular*}
    \vspace{-5pt}
}

\newcommand{\resumeScholarship}[4]{
    \vspace{-1pt}\item
        \begin{tabular*}{0.89\textwidth}{l@{\extracolsep{\fill}}r}
            \textbf{\small#1} & #2 \\
            \textit{\small#3} & \small #4 \\
        \end{tabular*}\vspace{-5pt}
    \vspace{0.3cm}
}

\newcommand{\resumeWorkshops}[4]{
    \vspace{-1pt}\item
        \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
            \textbf{\small#1} & #2 \\
            \textit{\small#3} & \small #4 \\
        \end{tabular*}\vspace{-5pt}
    \vspace{0.1cm}
}

\newcommand{\resumeCertifications}[4]{
    \vspace{-1pt}\item
        \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
            \textbf{\small#1} & #2 \\
            \textit{\small#3} & \small #4 \\
        \end{tabular*}\vspace{-5pt}
    \vspace{0.1cm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------

\textbf{\huge Daniel Brito} \\ 
\vspace{0.1cm} % Space between sections
\textbf{Software Engineer • Visual Artist • Writer} \\
\vspace{0.3cm} % Space between sections

%----------Location and contacts-----------------
\begin{tabular}{c c c c c}
    \faMapMarker{\hspace{0.1cm} Ceará, Brazil} & \hspace{0.45cm}
    \faEnvelope{\hspace{0.2cm}\href{mailto:danielhbrito@outlook.com}{danielhbrito@outlook.com}} & \hspace{0.45cm}
    \faLinkedin{\hspace{0.2cm}\href{https://www.linkedin.com/in/daniel-brito}{daniel-brito}} & \hspace{0.45cm}
    \faGlobe{\hspace{0.2cm}\href{https://danielbrito.github.io}{danielbrito.github.io}} & \hspace{0.45cm}
    \faPaperPlane{\hspace{0.2cm}\href{https://t.me/danielhbrito}{danielhbrito}}
\end{tabular}

\vspace{0.5cm} % Space between sections

% Justifying all the content:
\justify

%--------PROFILE------------
\section{\faUser \hspace{0.2cm} \Large Profile}

Software engineer with 3\texttt{+} years of experience, passionate about challenges that involve learning, sharing knowledge, and creating things, both in the fields of Art and Technology. Currently, having a greater interest in topics related to Software Architecture.

\vspace{0.3cm} % Space between sections

%-----------EXPERIENCE-----------------
\section{\faBriefcase \hspace{0.2cm} \Large Experience}

    \resumeSubHeadingListStart
        \resumeSubheading
        {Software Engineer}{\faCalendar \hspace{0.1cm} Apr 2021 - Currently}
        {OSF Digital}{\faMapMarker \hspace{0.1cm} Québec, CA - Remote}
        \begin{itemize}
            \item Development of web and mobile applications within high-performance teams from big companies and startups such as Caixa, Porto Seguro, and Creditas, mainly related to finance and innovation.
        \end{itemize}
    \resumeSubHeadingListEnd
    
    \vspace{-0.2cm}
    
    \resumeSubHeadingListStart
        \resumeSubheading
        {Research Assistant Intern}{\faCalendar \hspace{0.1cm} Feb 2022 - Apr 2022}
        {Laboratory of Studies and Research in Social Economics (LEPES/USP)}{\faMapMarker \hspace{0.1cm} Ribeirão Preto, SP - Remote}
        
        \begin{itemize}
            \item Developed a web platform addressing the issue ``enhancing the use and interpretation of data'' proposed during the HackPI - Hackathon for the First Childhood, performing data analysis from CSV files and plotting charts with more understandable results to help identify and implement public policy programs.
        \end{itemize}
    \resumeSubHeadingListEnd
    
    \vspace{-0.2cm}

    \resumeSubHeadingListStart
        \resumeSubheading
        {Software Developer Intern}{\faCalendar \hspace{0.1cm} Jan 2020 - Dec 2020}
        {ASTEF Foundation}{\faMapMarker \hspace{0.1cm} Fortaleza, CE - Remote}
        
        \begin{itemize}
            \item Developed web and mobile applications to optimize the patient admission process at Pró-Hemoce Institute. Some features include user management, notifications, an image gallery, a chatbot, and the generation of reports. Despite the affinity to learn front-end subjects, there was also a contact with concepts and tools related to UI/UX Design, back-end, and DevOps, as well as some agile methodologies principles.
        \end{itemize}

        \vspace{0.1cm} % Space between sections
    \resumeSubHeadingListEnd

%--------SKILLS------------
\section{\faPuzzlePiece \hspace{0.2cm} \Large Skills \& Interests}

    Knowledge acquired while working as a software engineer, besides other topics from a personal study guide. \href{https://github.com/DanielBrito/self-learning}{\scriptsize \faExternalLink}
    
    \resumeSubHeadingListStart
        \resumeSubItem {Programming Languages:}{\textit{Kotlin}, \textit{JavaScript}, Dart, Java, C++, Python, Processing, C.}
        \resumeSubItem {Front-end:}{\textit{HTML}, \textit{CSS}, \textit{ReactJS}, \textit{TypeScript}, Material UI, Styled Components, Bootstrap.}
        \resumeSubItem {Back-end:}{\textit{Spring Framework}, \textit{AWS}, \textit{Kafka}, \textit{Flyway}, \textit{GraphQL}, \textit{PostgreSQL}, \textit{JWT}, \textit{Swagger}, Firebase, NodeJS.}
        \resumeSubItem {Mobile:}{Flutter, React Native, Android.}
        \resumeSubItem {Testing:} {\textit{JUnit}, \textit{WireMock}, \textit{AssertJ}, \textit{MockK}, \textit{SonarQube}, \textit{Localstack}, \textit{React Testing Library}, Cypress.}
        \resumeSubItem {Monitoring:} {\textit{Datadog}, \textit{Opsgenie}, \textit{Amazon CloudWatch}, New Relic, Kibana.}        
        \resumeSubItem {DevOps:}{\textit{Git}, \textit{GitHub}, \textit{Docker}, CircleCI, Azure, GitLab.}
        \resumeSubItem {Tools:}{\textit{IntelliJ IDEA}, \textit{VS Code}, \textit{DBeaver}, \textit{Postman}, \textit{Jira}, \textit{Redash}, \textit{Split.io}.}
        \resumeSubItem {Design:}{Figma, Photoshop, Adobe XD, Inkscape, Blender, Balsamiq.}
        \resumeSubItem {Subjects:}{\textit{Software Architecture}, \textit{Design Patterns}, \textit{TDD}, \textit{DDD}, \textit{Data Structures}, \textit{Kanban}, Scrum, UI/UX.}
        \resumeSubItem {Soft Skills:}{\textit{Communication}, \textit{teamwork}, \textit{organization}, \textit{time management}, \textit{creativity}, \textit{critical thinking}.}
        
        \vspace{0.6cm} % Space between section
    \resumeSubHeadingListEnd

%--------LANGUAGES------------
\section{\faComments \hspace{0.2cm} \Large Languages}

\begin{tabular}{c c c c}
    \textbf{Portuguese:} Native & \hspace{0.5cm}
    \textbf{English:} B2 Upper Intermediate & \hspace{0.5cm}
    \textbf{Spanish:} A2 Elementary & \hspace{0.5cm}
    \textbf{French:} A1 Beginner
\end{tabular}

% \vspace{0.7cm} % Space between sections

%-----------EDUCATION-----------------
\section{\faGraduationCap \hspace{0.2cm} \Large Education}

    \resumeSubHeadingListStart
        \resumeSubheading
        {B.S. Computer Science \href{http://lattes.cnpq.br/6587136026055239}{\scriptsize \faExternalLink}}{\faCalendar \hspace{0.1cm} 2017 - 2021}
        {Federal University of Ceará (UFC)}{\faMapMarker \hspace{0.1cm} Crateús, CE}
        \begin{itemize}
            \item \textbf{Scholarships}
                \begin{itemize}
                    \resumeScholarship
                    {Program for Beginning Teachers:}{}
                    {Academic mentoring for IT and engineering students using C and Python.}{}
            
                    \resumeScholarship
                    {Program of Academic Initiation:}{}
                    {Practical studies of 3D modeling and Virtual Reality using Blender.}{}

                    \resumeScholarship
                    {Program of Academic Initiation:}{}
                    {Front-end development of educational platform using Semantic UI and AngularJS.}{}
                \end{itemize}
        \end{itemize}
        
        \vspace{-0.2cm}
      
        \begin{itemize}
            \item \textbf{Volunteer}
                \begin{itemize}
                    \item \textbf{GEMP/CRT:} Study group for the SBC Programming Marathon. \href{https://github.com/GEMP-UFC-Crateus}{\scriptsize \faExternalLink}
                    \item \textbf{Fire Tasks:} Workshop to build a task manager with ReactJS and Firestore. \href{https://github.com/DanielBrito/fire-tasks}{\scriptsize \faExternalLink}
                \end{itemize}
        \end{itemize}

        \vspace{0.05cm} % Space between sections
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{\faRocket \hspace{0.2cm} \Large Projects}

    \resumeSubHeadingListStart
        \resumeSubItem{Technology}{}
            \begin{itemize}
                \item \textbf{HáLugar:} Android app to help students share housing, built with Java, Google Maps, and Firebase. \href{https://play.google.com/store/apps/details?id=br.ufc.crateus.halugar}{\scriptsize \faExternalLink}
                \item \textbf{Dissertation:} Procedural modeling with Blender and Python. \href{https://github.com/DanielBrito/monografia}{\scriptsize \faExternalLink}
                \item \textbf{Compixelar:} Development of multimedia experiments using p5.js and Processing. \href{https://medium.com/@danielhbrito}{\scriptsize \faExternalLink}
            \end{itemize}
            
        \resumeSubItem{Education}{}
            \begin{itemize}
                \item \textbf{sTuring:} Scientific divulgation on topics related to Computing. \href{https://www.instagram.com/sturing.compsci/}{\scriptsize \faExternalLink}
                \item \textbf{YouTube Channel:}  Programming tutorials for beginners. \href{https://www.youtube.com/channel/UC4y3uq1d7MKDYs1LbI44Vng}{\scriptsize \faExternalLink}
            \end{itemize}
            
        \resumeSubItem{Arts}{}
            \begin{itemize}
                \item \textbf{Aluminions:} Creation of characters using aluminum seals. \href{https://www.instagram.com/aluminions.13/}{\scriptsize \faExternalLink}
                \item \textbf{Fanzines:} Electronic publication of poems. \href{https://drive.google.com/drive/folders/0BwdGPIUP6mG3dEl6cmRvWGJ6TzQ}{\scriptsize \faExternalLink}
            \end{itemize}

            \vspace{0.1cm} % Space between sections
    \resumeSubHeadingListEnd

%-----------AWARDS-----------------
\section{\faTrophy \hspace{0.2cm} \Large Awards}
    \resumeSubHeadingListStart
        \resumeSubItem{CEO Awards - Rising Star:}{Recognition for the remarkable work performed at OSF Digital as a Software Developer.}
        
        \vspace{-0.2cm}
        
        \resumeSubItem{Champion at HackPI Ceará:}{Hackathon promoted by the Federal University of Ceará (UFC) and the State Education Department (SEDUC) along with the University of São Paulo (USP), in which the participants should think of ways to address the issue of ``enhancing the use and interpretation of data''.}
        
        \vspace{0.2cm}
        
        \resumeSubItem{First Place at FIT.ON:}{Hackathon promoted by the Federal University of Ceará (UFC) during the Innovation and Technology Forum, in which the participants should think of solutions to connect small farmers to the market.}
        
        \vspace{0.2cm}
        
        \resumeSubItem{Best IT Work at University Meetings:}{Project ``Practical studies of 3D modeling and Virtual Reality using Blender'', which shows application of these concepts in digital art, animation, architecture, and game development.}
        
        \vspace{0.5cm}
    \resumeSubHeadingListEnd

%-----------OTHER INTERESTS-----------------
\section{\faThumbsUp \hspace{0.2cm} \Large Hobbies}

    Generative design, chess, astronomy, philosophy, literature, mathematics, history, poetry, calisthenics, running, skateboarding, cycling, music, gaming, cinema, traveling, researching, and blogging.
  
%-------------------------------------------
\end{document}
